simulation & inference of transients

### 2019-07-19 notebook/may-outbreak-ghost.Rmd
Examples of learning under different priors.
With a wide prior, the decision-maker acts optimally to squash the outbreak early on. The decision-maker never really learns for sure if this was the right decision (i.e. if this was really necessary or if the outbreak would have stopped at low level), it is basically a precautionary reaction -- the posterior belief remains broad since learning opportunity is lost by crushing the outbreak.

In contrast, the decision-maker with a prior more confident in a low-level stable state (i.e. mistaking past evidence of the "ghost" for a stable state), fails t

```{r}
damage <- 0.05
control <- 1
reward_fn <- function(x,h) - damage * x ^ 2 - control * h
discount <- 0.95

@@

```{r}
possible_a <- seq(.25, .34, by = 0.005)
true_a <- 0.26   ## reality has just a transient.  use  0.277 for stronger ghost
believe_a <- 0.31 ## believe there's an attractor
true_i <- which.min(abs(possible_a - true_a))
```

@@

```{r, results="hide"}
soln <- mdp_value_iteration(m$transition, m$reward, discount)

opt_soln <- mdp_value_iteration(m_true$transition, m_true$reward, discount)

@@

Optimal strategy knowing this is just a transient:

@@

df <- mdp_planning(m_true$transition, m_true$reward, discount, model_prior = c(1), 
                   policy = opt_soln$policy, x0 = x0, Tmax = 400)

@@

```{r}
prior <- dnorm(possible_a, believe_a, 0.03)
prior <- prior / sum(prior)
```

>>>>

```{r}
damage <- 0.05
control <- 1
reward_fn <- function(x,h) - damage * x ^ 2 - control * h
discount <- 0.98

@@

```{r}
possible_a <- seq(.25, .34, by = 0.005)
true_a <- 0.27   ## reality has just a transient.  use  0.277 for stronger ghost
believe_a <- 0.29 ## believe there's an attractor
true_i <- which.min(abs(possible_a - true_a))
```

@@

```{r, results="hide"}
soln <- mdp_value_iteration(m$transition, m$reward, discount)
opt_soln <- mdp_value_iteration(m_true$transition, m_true$reward, discount)

@@

Optimal strategy knowing this is just a transient (will depend on discount rate):

@@

df <- mdp_planning(m_true$transition, m_true$reward, discount, model_prior = c(1), 
                   policy = opt_soln$policy, x0 = x0, Tmax = 100)

@@

```{r}
prior <- dnorm(possible_a, believe_a, 0.01)
prior <- prior / sum(prior)
```
